Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-15 programlogic.tex
tiny soundness section

>>>>

\subsection{Soundness}
Our rules from Figure \ref{fig:wpdamd} are proven sound in Iris against an assembly-level hardware model
implementing a fragment of x86-64 including 64-bit address translation with 4-level page tables.

At the moment our proofs do rely on 11 small axioms of properties which should be provable, but
are challenging to discharge due to some representation choices in our model.\footnote{See \texttt{srx/x64/machine/current_axioms.v}}
